Process_OlisJazEmData

### 2024-01-08 Code/Process_OlisJazEmData.Rmd
removed extra lines

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE}

@@

Project <- "PICO"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
DataInOlis <- file.path("..", "Data", "ImportedData", "ImportedOlisData", fsep = .Platform$file.sep)
DataInJaz <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "Output", "Plots")

>>>>

# Load Libraries
```{r load libraries, warning = FALSE, echo=FALSE}

@@

Project <- "PICO"

DataInOlis <- file.path("..", "Data", "ImportedData", "ImportedOlisData", fsep = .Platform$file.sep)
DataInJaz <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
PlotsPath <- file.path("..", "Output", "Plots")
